\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-05-04 paper_final.tex
small change
Added more recent references

\section{Introduction}
There may be a scenario where one entity, or the \textit{teacher},  has a desired target concept and a learner in which the teacher wants to embed that concept. In this scenario the teacher can only interact with the learner by constructing and then giving the learner a set of training examples. This constructive task is known as optimal teaching \cite{machine_teaching} \cite{teaching_dimension}. \cite{perceptron} looked for the first time at online teaching in an online environment, with an online perceptron. In this paper we look at optimal teaching of the same perceptron, but now we give the teacher the ability to use unlabeled examples. Unlabeled examples allow the teacher to probe to discover more about the learners current state while not changing the learner. We show that this new added ability allows the teacher to teach an online perceptron in a scenario, that before may have been difficult.

>>>>

\section{Introduction}
There may be a scenario where one entity, or the \textit{teacher},  has a desired target concept and a learner in which the teacher wants to embed that concept. In this scenario the teacher can only interact with the learner by constructing and then giving the learner a set of training examples. This constructive task is known as optimal teaching \cite{machine_teaching} \cite{teaching_dimension}. It has applications in education and security \cite{security}\cite{education} \cite{poisoning}. \cite{perceptron}\cite{td_linear} looked for the first time at online teaching in an online environment, with an online perceptron. In this paper we look at optimal teaching of the same perceptron, but now we give the teacher the ability to use unlabeled examples. Unlabeled examples allow the teacher to probe to discover more about the learners current state while not changing the learner. We show that this new added ability allows the teacher to teach an online perceptron in a scenario, that before may have been difficult.
